---
title: "NYCFlights: Arrival Delay Regression Model"
author: "Andrew Ju""
date: "10/17/2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
install.packages("psych")
library(psych)
library(readr)
```

# NYCFlights Model

Using the rectangular data that you created last week and following the *Predicting Medical Expenses* example from the text (*MLwR*), create a model for arr_delay. Follow MLwR structure 
for building a model. Describe/Explain each of the steps and show all work in codeblocks below.


## Step 1: Collect Data 

```{r "Step 1: Collect Data" }
#write.csv(joined_data, file = "C:/Users/aju/Desktop/CSX460/03-linear-regression/HW2_joined_data.csv")

joined_data <- read_csv("C:/Users/aju/Desktop/CSX460/03-linear-regression/HW2_joined_data.csv")
head(joined_data)

```

## Step 2: Explore and Prep The Data


One of the things not done in the MLwR text is a pairwise comparison between the response and each of the predictors. Make sure to do this; this is often very illustrative of the relationship between that predictor and the response. This can be done with `pairs` or `psych::panel.pairs`


```{r "Step 2: Explore and Prep The Data" }

str(joined_data)
sum(is.na(joined_data$arr_delay))/length(joined_data$arr_delay)
# 02.8% NAs

qplot(joined_data$arr_delay)

IQR(joined_data$arr_delay, na.rm = TRUE)
fivenum(joined_data$arr_delay, na.rm = TRUE)

boxplot(joined_data$arr_delay)

?cor
is.numeric(joined_data$arr_delay)
is.numeric(joined_data$dep_delay)

cor(joined_data$arr_delay, joined_data$dep_delay, use = "complete.obs")
cor(joined_data[c("arr_delay", "dep_delay", "distance")], use = "complete.obs")


?apply
#sapply(joined_data, is.numeric) %>% pairs() 
joined_data_num <- joined_data[, sapply(joined_data, is.numeric)]
cor(joined_data_num, use = "complete.obs")

head(joined_data_num)

par(mar = c(1,1,1,1))
pairs(joined_data_num[1:10])
?par
# issue where just too many graphs at once? getting "Error in plot.new() : figure margins too large"

pairs(joined_data[c("arr_delay", "dep_delay")])
psych::pairs.panels(joined_data[c("arr_delay", "dep_delay", "distance")])
pairs(joined_data)
# performance on pairs ... seems awfully slow

```

## Step 3:  Train The Model

```{r "Step 3: Train The Model" }
model_1 <- lm (data = joined_data, dep_delay ~ .)
# contrasts can be applied only to factors with only 2 or more levels --> so drop single factor variables, I'm assuming

check <- sapply(joined_data, function(x)is.factor(x))
check
# !!!!! question
# not working ... how to check if variables are single factor variables? --> needed to export to CSV and manually check ... 
# excluding tz.x & dst.x

single_factor_vars <- names(joined_data) %in% c("tz.x", "dst.x", "year.x", "dst.y")
joined_data_model <- joined_data[!single_factor_vars]

joined_data_model[c("carrier", "origin", "dest", "type", "manufacturer", "model", "engine", "name.x", "name.y")] <- lapply(joined_data_model[c("carrier", "origin", "dest", "type", "manufacturer", "model", "engine", "name.x", "name.y")], factor)

#joined_data_model[,factors] <- lapply(joined_data_model[,factors], factor)
# ^doesn't work, bad internet advice 

joined_data_model_no_na <- na.omit(joined_data_model)
str(joined_data_model)

# lm( data=joined_data_model, dep_delay ~ arr_delay + carrier + origin + dest + model + distance + precip)
# lm does work, just needed to double check with the dist.y variable being a single factor

model_2 <- lm (data = joined_data_model_no_na, dep_delay ~ .)
summary(model_2)

model_3 <- lm(data = joined_data_model, dep_delay ~ .)
summary(model_3)


```

## Step 4: Evaluate Performance

Evaluating performance is a crutial step, that has yet to be treated well by the MLwR. Think about some of the tools that you have for evaluating performance.  Choose one and articulate why you have chosen it.

```{r "Step 4: Evaluate Performance" }

```


## Step 5: Improve Performance 

Show some steps for improving model performance.

```{r "Step 5: Improve Performance" }


```


# Question:

Is this a good model?  (Write your answer here.)

