---
title: "NYCFlights: Arrival Delay Logictic Model"
author: "Andrew Ju"
date: "10/25/2016""
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(dplyr)
library(psych)
library(readr)
library(MASS)

```


## Logsitic and Inverse Logistic Transformation 

- Write an R function for the logistic function. The function should accept a `numeric` vector with values `[-Inf,Inf]` and produce a numeric vector in the the range `[0,1]`.

- Plot the logistic function from  `[-10,10]`

- Write a R function for the inverse logistic function. The function should accept a `numeric` vector with values `[0,1]` and prodcuce a numeric vector in the range `[-Inf,Inf]`

- Plot the Inverse Logistic function from `[0,1]`


**Hint:** For plotting curves see `?graphics::curve` or `?ggplot2::stat_function`

```{r "Logistic and Inverse Logistic" }
 
logistic <- function(x)
  (x/(1-x))

logistic(c(-Inf,0,Inf)) %>% qplot(geom = ("density"))



inverse_logistic <- function(x)
  log(x/(1-x))

inverse_logistic(c(-1,1)) %>% qplot


```


# NYCFlights Model

Using the rectangular data that you created from assignment and following the *Predicting Medical Expenses* example from the text (*MLwR*), create a model for arr_delay >= 15 minutes. Follow *MLwR* structure   for building a model. Describe/Explain each of the steps and show all work in codeblocks below.

KNIT YOUR DOCUMENT AS *HTML* AND SUBMIT IT AND THE `Rmd` file.   

## Step 1: Collect Data 

```{r "Step 1: Collect Data" }

#write.csv(joined_data, file = "C:/Users/aju/Desktop/CSX460/03-linear-regression/HW2_joined_data.csv")

joined_data <- read_csv("C:/Users/Andrew Ju/CSX460 - Fall2016/03-linear-regression/HW2_joined_data.csv")
head(joined_data)



```

## Step 2: Explore and Prep The Data


One of the things not done in the MLwR text is a pairwise comparison between the response and each of the predictors. Make sure to do this; this is often very illustrative of the relationship between that predictor and the response. This can be done with `pairs` or `psych::panel.pairs`


```{r "Step 2: Explore and Prep The Data" }

str(joined_data)
sum(is.na(joined_data$arr_delay))/length(joined_data$arr_delay)
# 02.8% NAs

# SHOULD LOOK AT SKEW NEXT TIME TOO
# not a bad idea to come up with hypotheses for strong predictors before even modeling
qplot(joined_data$arr_delay)

IQR(joined_data$arr_delay, na.rm = TRUE)
fivenum(joined_data$arr_delay, na.rm = TRUE)

boxplot(joined_data$arr_delay)

?cor
is.numeric(joined_data$arr_delay)
is.numeric(joined_data$dep_delay)

cor(joined_data$arr_delay, joined_data$dep_delay, use = "complete.obs")
cor(joined_data[c("arr_delay", "dep_delay", "distance")], use = "complete.obs")


?apply
#sapply(joined_data, is.numeric) %>% pairs() 
joined_data_num <- joined_data[, sapply(joined_data, is.numeric)]
cor(joined_data_num, use = "complete.obs")

head(joined_data_num)

par(mar = c(1,1,1,1))
pairs(joined_data_num[1:10])
?par
# issue where just too many graphs at once? getting "Error in plot.new() : figure margins too large"

pairs(joined_data[c("arr_delay", "dep_delay")])
psych::pairs.panels(joined_data[c("arr_delay", "dep_delay", "distance")])
pairs(joined_data)
# performance on pairs ... seems awfully slow



```

## Step 3:  Train The Model

```{r "Step 3: Train The Model" }

log_joined_data <- joined_data_model_no_na[]


```

## Step 4: Evaluate Performance

Think about some of the tools that you have for evaluating performance.  Choose one and articulate why you have chosen it.

```{r "Step 4: Evaluate Performance" }

```

 
## Step 5: Improve Performance 

Show some steps for improving model performance.

```{r "Step 5: Improve Performance" }

```


# Question:

Is this a good model?  (Write your answer here.)


# PART B:

Your model should be good at explaining tardiness. Now, assume that your job is to predict arrival delays a month in advance. You can no longer use all the features in your model. Retrain your model using only features that will be *known* only a month in advance of the departure time.  Show all steps as above.

